Modelling the emergence of whisker barrels

### 2019-12-19 paper/briefpaper/brief.tex

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{../briefpaper/MainFig.pdf}
\end{center}
\caption{\textbf{A} Left shows a cytochrome oxidase stain obtained from rat S1 by \cite{zheng_signal_2001}, with black lines to delineate barrels and to measure departure ($\delta$) from a perfect Voronoi tesselation. Right shows the initial distribution of axon branching density ($a$) for one thalamocortical projection and two molecular guidance fields ($\rho$). \textbf{B} The strength of interaction $\gamma$ for each of 41 projections with field $\rho_1$ and $\rho_2$ are indicated by the lengths of green and blue arrows respectively, assuming that similar fields aligned to the posterior-anterior and medial-lateral axes in the ventroposterior medial nucleus of the thalamus are sampled at the locations of barreloid centers (reconstructed from \cite{haidarliu_size_2001}). \textbf{C} Simulation results for parameters $N=41$, $\alpha=3$, $\beta=20$, $k=3$, $D=0.2$, $\gamma\in\pm 2$ and $\delta{t}=0.0001$. Colours indicate the thalamic projection for which the connection density is maximal, black lines delineate boundaries, and overlaid contours show $c>0.2$. \textbf{D} The Honda $\delta$ metric (red dots; see \cite{senft_mouse_1991}) measures departure from a Voronoi tesselation (dotted line corresponds to the barrels in $A$), and $\eta$ (black squares) measures the correspondence between the real and simulated barrel shapes (the product of the sum of squared differences between real and simulated centers and the sum of squared differences in area; units mm$^4$). \textbf{F.} Guidance fields and emergent barrel pattern in a Fgf8 misexpression experiment (c.f. \cite{assimacopoulos_fibroblast_2012}), simulated by reflecting $\rho_1$ about the anterior-posterior axis. All scale bars 1mm.}
\label{fig:main}
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{./MainFig.png}
\end{center}
\caption{\textbf{A} Left shows a cytochrome oxidase stain obtained from rat S1 by \cite{zheng_signal_2001}, with black lines to delineate barrels and to measure departure ($\delta$) from a perfect Voronoi tesselation. Right shows the initial distribution of axon branching density ($a$) for one thalamocortical projection and two molecular guidance fields ($\rho$). \textbf{B} The strength of interaction $\gamma$ for each of 41 projections with field $\rho_1$ and $\rho_2$ are indicated by the lengths of green and blue arrows respectively, assuming that similar fields aligned to the posterior-anterior and medial-lateral axes in the ventroposterior medial nucleus of the thalamus are sampled at the locations of barreloid centers (reconstructed from \cite{haidarliu_size_2001}). \textbf{C} Simulation results for parameters $N=41$, $\alpha=3$, $\beta=20$, $k=3$, $D=0.2$, $\gamma\in\pm 2$ and $\delta{t}=0.0001$. Colours indicate the thalamic projection for which the connection density is maximal, black lines delineate boundaries, and overlaid contours show $c>0.5$. \textbf{D} The Honda $\delta$ metric (red dots; see \cite{senft_mouse_1991}) measures departure from a Voronoi tesselation (dotted line corresponds to the barrels in $A$), and $\eta$ (black squares) measures the correspondence between the real and simulated barrel shapes (the product of the sum of squared differences between real and simulated centers and the sum of differences in area; units mm$^4$). \textbf{E.} Guidance fields and emergent barrel pattern in a Fgf8 misexpression experiment (c.f. \cite{assimacopoulos_fibroblast_2012}), simulated by reflecting $\rho_1$ about the anterior-posterior axis. All scale bars 1mm.}
\label{fig:main}
\end{figure*}
